ICS Phenotyping

### 2019-07-02 ICS_Phenotyping.Rmd
boolean graphs for phenotype

```{r}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
```

@@

#for me
for(key in keynames){
    print(key)
    #will bind together into a new dataframe the columns that contain the key in the name from
    #1. the original entries in the mimosa data frame, 2. the untouched phenotype data and 3. the new phenotype data with NA values
    test<-data.frame(cbind(mimosa[grep(key, names(mimosa))], 
                           phenotype[grep(paste(key,"_",sep=""), names(phenotype))],
                           DF[grep(paste(key,"_",sep=""), names(DF))]))
    #how many rows in the data have a 0 indicating they aren't a real response and have data in the corresponding columns of the phenotype data --> should be substantial
    print(length(which(test[,8]==0 &! is.na(test[,9:24]))))
        #how many rows in the data have a 0 indicating they aren't a real response and have data in the corresponding columns of the modified phenotype data --> should be 0
    print(length(which(test[,8]==0 &! is.na(test[,25:40]))))
}

@@

```{r}
test<-mutate_TB(filter(DF, !is.na(TH1_GATA3)))
kable(xtabs(~TB+SM, test))
plot_2(test, "disease", "TH1_GATA3")
plot_2(test, "disease", "TH1_t_x_x_4")
plot_2(test, "disease", "TH1_t_x_x_x")
plot_2(test, "disease", "TH1_x_g_3_4")
plot_2(test, "disease", "TH1_x_g_3_x")
plot_2(test, "disease", "TH1_x_g_x_4")
plot_2(test, "disease", "TH1_x_x_3_x")

grid.arrange(plot_2(test, "disease", "TH1_t_x_x_x")+labs(y="Tbet+ CD4+ T cells"),
plot_2(test, "disease", "TH1_t_x_x_4")+labs(y="CCR4+Tbet+ CD4+ T Cells (%)"),
    plot_2(test, "disease", "TH1_GATA3")+labs(y="GATA3+ CD4+ T cells (%)"),
ncol=3
)
```

@@

```{r example ggplot}
library(ggplot2)
data<-filter(phenotype, Stim %in% c("PMA", "PEP", "WCL"))
data$Stim<-factor(data$Stim, levels=c("PMA","PEP","WCL"))
colnames<-names(data)[grep("TH1_", names(data))]
for(col in colnames){
    y<-plot_stim(data, col)
    print(y)
    }    
```

>>>>

```{r}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
```

@@

#for me
for(key in keynames){
    print(key)
    #will bind together into a new dataframe the columns that contain the key in the name from
    #1. the original entries in the mimosa data frame, 2. the untouched phenotype data and 3. the new DF<-subset(CD4, CD4$Stim=="PEP")
    test<-data.frame(cbind(mimosa[grep(key, names(mimosa))], 
                           phenotype[grep(paste(key,"_",sep=""), names(phenotype))],
                           DF[grep(paste(key,"_",sep=""), names(DF))]))
    #how many rows in the data have a 0 indicating they aren't a real response and have data in the corresponding columns of the phenotype data --> should be substantial
    print(length(which(test[,8]==0 &! is.na(test[,9:24]))))
        #how many rows in the data have a 0 indicating they aren't a real response and have data in the corresponding columns of the modified phenotype data --> should be 0
    print(length(which(test[,8]==0 &! is.na(test[,25:40]))))
}

@@

```{r, fig.width=16, fig.height=8}
test<-mutate_TB(filter(DF, !is.na(TH1_GATA3)))
test2<-melt(test, id.vars=c("Donor", "TB", "SM", "Stim"), measure.vars = grep("TH1_._._._.", names(DF)))
test2<-filter(test2, variable!="TH1_x_x_x_x")
test2$variable<-gsub("TH1_", "", test2$variable)
ggplot(test2, aes(x=variable, y=value, fill=TB, alpha=SM))+
    geom_boxplot()+
    scale_alpha_manual(values=c(0.5,1))+
    scale_fill_manual(values =c("#2166ac", "#b2182b"))+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    theme(legend.position="none")+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(title="Lineage Marker Expression on Mtb-Specific TH1 CD4+ T cells",
         y="Frequency of Marker+ Mtb-Specific T cells")
kable(xtabs(~TB+SM, test))
```

```{r, fig.width=16, fig.height=8}
test<-mutate_TB(filter(DF, !is.na(TH2_GATA3)))
test2<-melt(test, id.vars=c("Donor", "TB", "SM", "Stim"), measure.vars = grep("TH2_._._._.", names(DF)))
test2<-filter(test2, variable!="TH2_x_x_x_x")
test2$variable<-gsub("TH2_", "",test2$variable)
ggplot(test2, aes(x=variable, y=value, fill=TB, alpha=SM))+
    geom_boxplot()+
    scale_alpha_manual(values=c(0.5,1))+
    scale_fill_manual(values =c("#2166ac", "#b2182b"))+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    theme(legend.position="none")+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(title="Lineage Marker Expression on Mtb-Specific TH2 CD4+ T cells",
         y="Frequency of Marker+ Mtb-Specific T cells")
kable(xtabs(~TB+SM, test))
```

```{r}
test<-mutate_TB(filter(DF, !is.na(TH1_GATA3)))
kable(xtabs(~TB+SM, test))
plot_2(test, "disease", "TH1_GATA3")
plot_2(test, "disease", "TH1_t_x_x_4")
plot_2(test, "disease", "TH1_t_x_x_x")
plot_2(test, "disease", "TH1_x_g_3_4")
plot_2(test, "disease", "TH1_x_g_3_x")
plot_2(test, "disease", "TH1_x_g_x_4")
plot_2(test, "disease", "TH1_x_x_3_x")
plot_2(test, "disease", "TH1_GATA3CXCR3")
plot_2(test, "disease", "TH1_GATA3CCR4")
```

```{r, fig.width=12, fig.height=6}
grid.arrange(plot_2(test, "disease", "TH1_t_x_x_x")+labs(y="Tbet+ CD4+ T cells"),
plot_2(test, "disease", "TH1_t_x_x_4")+labs(y="CCR4+Tbet+ CD4+ T Cells (%)"),
    plot_2(test, "disease", "TH1_GATA3")+labs(y="GATA3+ CD4+ T cells (%)"),
ncol=3
)
```

@@

```{r example ggplot}
library(ggplot2)
data<-mutate_TB(filter(phenotype, Stim %in% c("PMA", "PEP", "WCL")))
data$Stim<-factor(data$Stim, levels=c("PMA","PEP","WCL"))
colnames<-names(data)[grep("TH1_", names(data))]
for(col in colnames){
    y<-plot_stim(data, col)
    print(y)
    }    
```
